Polyglots: Crossing Origins by Crossing Formats

### 2013-08-26 main.tex
no message

\permission{Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than ACM must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from permissions@acm.org.}
\conferenceinfo{CCS'13,}{November 4--8, 2013, Berlin, Germany.}
\copyrightetc{Copyright 2013 ACM \the\acmcopyr}
\crdata{978-1-4503-2477-9/13/11\ ...\$15.00.\\
http://--enter the whole DOI string from rightsreview form confirmation}

@@

\numberofauthors{3}
\author{\alignauthor
Jonas Magazinius\\
\affaddr{Department of Computer Science}\\
\affaddr{Chalmers University of Technology}\\
\affaddr{Gothenburg, Sweden}\\
\email{jonas.magazinius@chalmers.se}
\alignauthor 
Billy K. Rios\\
\affaddr{Cylance, Inc.}\\ 
\affaddr{Irvine, United States of America}\\ 
\email{billy.rios@gmail.com} 
\alignauthor
Andrei Sabelfeld\\
\affaddr{Department of Computer Science}\\ 
\affaddr{Chalmers University of Technology}\\ 
\affaddr{Gothenburg, Sweden}\\ 
\email{andrei@chalmers.se} 
}

@@

\category{H.4}{Information Systems Applications}{Miscellaneous}

\keywords{Web Security, Polyglot, Injection, Cross-domain}

@@

>>>>

\permission{Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than ACM must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from permissions@acm.org.}
\conferenceinfo{CCS'13,}{November 4--8, 2013, Berlin, Germany.}
\copyrightetc{Copyright 2013 ACM \the\acmcopyr}
\crdata{978-1-4503-2477-9/13/11\ ...\$15.00.\\
 http://dx.doi.org/10.1145/2508859.2516685}

@@

\numberofauthors{3}
\author{\alignauthor
Jonas Magazinius\\
%\affaddr{Department of Computer Science}\\
\affaddr{Chalmers University of Technology}\\
\affaddr{Gothenburg, Sweden}\\
\email{jonas.magazinius@chalmers.se}
\alignauthor 
Billy K. Rios\\
\affaddr{Cylance, Inc.}\\ 
\affaddr{Irvine, CA, USA}\\ 
% \email{billy.rios@gmail.com} 
\alignauthor
Andrei Sabelfeld\\
%\affaddr{Department of Computer Science}\\ 
\affaddr{Chalmers University of Technology}\\ 
\affaddr{Gothenburg, Sweden}\\ 
\email{andrei@chalmers.se} 
}

@@

\category{K.6.5}{Security and Protection}{Unauthorized access}

\keywords{Web Security; Polyglot; Injection; Cross-domain}

@@

\section*{Acknowledgments}
This work was funded by 
the European Community under the ProSecuToR and WebSand projects
and
the Swedish research agencies SSF and VR.
